### 2014-02-27 paper/concrete.tex

Instead of using a configuration of the form
|iconf iS (fullconf id1 il1 tS1 ie1, fullconf id2 il2 tS2 ie2 ldots)|
where every task has its
own ML heap, we would like a single global heap as in
|oneheapiconf iS tS (oneheapfullconf id1 il1 ie1, oneheapfullconf id2 il2 ie2, ldots)|.
Furthermore, we keep up a fictional separation between the portions
of the global heap that tasks can use by forbidding references to
cross task boundaries. Most
of the operational rules can easily be adapted to work with these
new configurations.  In the abstract system, the \textsc{I-fork}
rule created a new heap for the new task to execute in.  Since we
want to forbid references to cross task boundaries, we do not modify
the global heap and instead add an additional premise that the forked
expression |ie| must not contain any references.
Finally, we add the same condition to the \textsc{I-send} rule.
Tasks that try to fork or send an expression that contains a
reference will now get stuck, and will stop executing by the
\textsc{I-noStep} rule.

@@

@@

\Red{isomorphism definition here}

Now, we propose the following two-step process to ensure that
TSNI is preserved:
\begin{enumerate}
  \item First, any of the reduction rules of the abstract
  semantics presented in Section~\ref{sec:retrofit} can
  be restricted by adding a predicate $P$ to the premise of
  any rule other than \textsc{I-noStep}.  The predicate $P$
  can depend only on the \textit{erased} configuration
  |erase il ic|, where |il| is the label of the first task
  in the task list.
\end{enumerate}

We now have a concrete semantics, which both uses a different
representation for some of the constructs in language (a single
heap rather than a heap per task in our running example), as well
as restricting some of the operational rules to disallow
undesirable transitions.  To show that the concrete semantics
still satisfy TSNI, we use two techniques.  First, we give a
condition on what kind of restrictions can be allowed on the
operational rules.  Secondly, we define the notation of an
isomorphism between IFC languages and show that it preserves
non-interference.

@@

\begin{definition}[Weak isomorphism of information-flow control languages]
    A language \con{|(C, .->, erasef l)|} is weakly isomorphic to a
    language \abs{|(iC, .->, erasef l)|} if there exist total functions
    |f : tC -> iC| and |finv : iC -> tC| such that |f .. finv = idf tC|
    |finv .. f = idf iC|.  Furthermore, the following coherence conditions
    must hold:
    \begin{itemize}
        \item |f| is functorial (e.g. if $\abs{x\ R\ y}$ then
            $f(\abs{x})\ \con{R}\ f(\abs{y})$) over both
            $l$-equivalences and |.->|, and
        \item |finv| is functorial over $l$-equivalence (though not necessarily |.->|).
    \end{itemize}
\end{definition}

>>>>

Instead of using a configuration of the form
|iconf iS (fullconf id1 il1 tS1 ie1, fullconf id2 il2 tS2 ie2 ldots)|
as is done in |specLangML alpha|
where every task has its
own ML heap, we would like a single global heap as in
|oneheapiconf iS tS (oneheapfullconf id1 il1 ie1, oneheapfullconf id2 il2 ie2, ldots)|.
Furthermore, we keep up a fictional separation between the portions
of the global heap that tasks can use by forbidding references to
cross task boundaries. Most
of the operational rules can easily be adapted to work with these
new configurations.  In the abstract system, the \textsc{I-fork}
rule created a new heap for the new task to execute in.  Since we
want to forbid references to cross task boundaries, we do not modify
the global heap and instead add an additional premise that the forked
expression |ie| must not contain any references.
Finally, we add the same condition to the \textsc{I-send} rule.
Tasks that try to fork or send an expression that contains a
reference will now get stuck, and will stop executing by the
\textsc{I-noStep} rule.
We call this family of languages |concreteLangMl alpha|, which
is still parametrized by the scheduling policy |alpha|.

@@

Next, we will make these two intuitions precise and give a general
definition for how non-interference can be preserved.  Then, we
show that the definition in Figure~\Red{XXX} satisfy these
conditions.

@@

\begin{definition}[Weak isomorphism of information-flow control languages]
  A language \con{|(C, .->, erasef l)|} is \textit{weakly isomorphic} to a
  language \abs{|(iC, .->, erasef l)|} if there exist total functions
  |f : tC -> iC| and |finv : iC -> tC| such that |f .. finv = idf tC|
  |finv .. f = idf iC|.  Furthermore, the following coherence conditions
  must hold:
  \begin{itemize}
    \item |f| is functorial (e.g. if $\abs{x\ R\ y}$ then
    $f(\abs{x})\ \con{R}\ f(\abs{y})$) over both
    $l$-equivalences and |.->|, and
    \item |finv| is functorial over $l$-equivalence (though not necessarily |.->|).
  \end{itemize}
  We furthermore call the two languages \textit{isomorphic} if both
  |f| and |finv| are functorial over |.->|.
\end{definition}

Now, we can propose the following two-step process to ensure that
TSNI is preserved:
\Red{We should find a better name for this, or not use a name, or something.}
\begin{definition}[Non-Interference preserving, restricted isomorphism (NPRI)]
  We call an IFC language
  |concreteLang alpha targetLang| (which can be thought of as
  the concrete language) a \textit{non-intereference preserving,
  restricted isomorphism} with regard to the IFC language
  |specLang alpha targetLang|
  (which can be thought of as the abstract language) if the following
  two conditions hold:
  \begin{enumerate}
    \item Any of the reduction rules of the abstract
    semantics |specLang alpha targetLang|
    presented in Section~\ref{sec:retrofit} can
    be restricted by adding a predicate $P$ to the premise of
    any rule other than \textsc{I-noStep}.  The predicate $P$
    can depend only on the \textit{erased} configuration
    |erase il ic|, where |il| is the label of the first task
    in the task list.
    \item The concrete language
    |concreteLang alpha targetLang|
    must be isomorphic to the abstract semantics |specLang alpha targetLang|
    with the additional predicates $P$ on the rules.
  \end{enumerate}
\end{definition}

\begin{theorem}[NPRI implies TSNI]
  If a language |concreteLang alpha targetLang| is a NPRI, then
  |concreteLang alpha targetLang| satisfies TSNI.
\end{theorem}

With this machinery in place, we can now state and prove that our
single-heap ML-like IFC language is NPRI, and thus non-interfering.

\begin{theorem}
  The language |concreteLangMl alpha| is a NPRI.
\end{theorem}
As a trivial corollary, it follows that |concreteLangMl roundrobinf| is
TSNI, and |concreteLangMl seqf| is TINI.

\begin{proof}
  It is easy to see that condition 1.\ of NPRI is satisfied, since
  we only add a side condition to the rules \textsc{I-fork} and
  \textsc{I-send}, and the condition only inspects the expression
  of the current task, which is by the definition of |erasef il| not
  erased.

  This leaves us to give an isomorphism between |concreteLangMl alpha|
  and |concreteLang alpha targetLangMl|, which we do as follows.
  \Red{Actually give an isomorphism.}
\end{proof}

@@
